Verifying Demonstrations

### 2019-02-26 paper/verifiability-analysis.tex
Edits temporal eligibility in security analysis

In general, to prevent replays, Alice must respond to an unpredictable 
challenge.
The challenge here is \enquote{which is the hash value of the head block of the 
  ledger at the time of the proof's creation?}.
The response is simply the hash itself (obtained through \(\TSget\)) and is 
included as \(t_s\) and \(t_s'\) in the proof share (see \cref{fig:ProofFig}).

As it is the case in the construction of ledgers, the hash value of the head 
block depends on the previous blocks.
Thus, the predictability of \(t_s\) depends on the predictability of the 
blocks, which depends on the predictability of the transactions.
Assume that Alice can control all transactions going into a block.
This means that she must find a pre-image of the form of a valid block that is 
accepted by all nodes in the distributed ledger.
\Ie it depends on the pre-image resistance of the hash function used.
Thus, with a collision resistant hash function (\(\Hash\)), Alice can predict 
\(t_s\) only with negligible probability; and it follows that, with high 
probability, \(t_s\) was published on the ledger before Alice included it in 
her proof share.

The correctness of the response must be verifiable by any verifier (verifiable 
through \(\TStime\)).
This can be done if the ledger is continuously extended at a fixed rate, \eg 
one new block every 10 minutes, as was the case for Bitcoin.

According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
The hash values of the proof shares are committed to the ledger, which means 
that there is a negligible probability that they were created after that.
Alice is in the same situation as above:
she would have to choose a value \(y\) in the range of the hash function 
\(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
is a valid proof for the desired protest, at the desired time.
If \(\Hash\) is collision resistant, finding \emph{any} pre-image is hard.

>>>>

In general, to prevent replays, Alice must respond to an unpredictable 
challenge.
The challenge here is \enquote{what did \(\TSget\) return at the time of the 
  proof's creation?}.
The response is included as \(t_s\) and \(t_s'\) in the proof share (see 
\cref{fig:ProofFig}).
The unpredictability of \(\TSget\) ensures that a proof cannot have been 
created before \(\max\{t_s, t_s'\}\).
The correctness of the response must be verifiable by any verifier, which is 
the case with \(\TStime\).

According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
The hash values of the proof shares are committed to the ledger (\(\TSstamp\)), 
which means that there is a negligible probability that they were created after 
that:
Alice would have to choose a value \(y\) in the range of the hash function 
\(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
is a valid proof for the desired protest, at the desired time.
If \(\Hash\) is collision resistant, she will succeed with negligible 
probability.
